Elephant Seal Age JAE Intraspecific Variation

### 2023-12-06 paper/paperv3.qmd
update with new feedback from Roxanne

sealdat <- read_csv(here::here("data/raw/128L pull 2023_11_30.csv"), 
                    show_col_types = FALSE) %>% 
  mutate(observed = if_else(observed == "B", "Breeder", "Non-breeder"), 
         observed_int = if_else(observed == "Breeder", 1, 0), 
         pup_survived = pupseeneveragain > 0,) %>% 
  filter(age > 3, 
         year > 1987)
```

@@

```{r}
#| tbl-cap: str_glue("The results from breeding probability analyis. The random effect variance of animal id is {VarCorr(breeding_mod, digits = 3)[1]} and year was VarCorr(breeding_mod, digits = 3)[2]".)
#| eval: true

@@

surv_recruit_data <- sealdat %>% 
  drop_na(pupID) %>% 
  filter(pupsex == "F",
         pupyearborn < 2016) %>% 
  mutate(pup_survived_dbl = ifelse(pup_survived, 1, 0)) %>% 
  group_by(age) %>% 
  mutate(n_pups = n()) %>% 
  ungroup() %>% 
  filter(n_pups >= 5)
pup_surv_model <- glmer(pup_survived_dbl ~ poly(age, 2) + (1 | year),
                        data = surv_recruit_data, 
                        family = "binomial")
pup_surv_pred <- ggpredict(pup_surv_model, terms = c("age [all]")) %>% 
  as_tibble() %>% 
  transmute(age = x, 
            metric = "surv", 
            mean = predicted, 
            mean_lwr = conf.low, 
            mean_upr = conf.high)
pup_recruit_model <- glmer(puprecruited ~ poly(age, 2) + (1 | year),
                           data = surv_recruit_data, 
                           family = "binomial")
pup_recruit_pred <- ggpredict(pup_recruit_model, terms = c("age [all]")) %>% 
  as_tibble() %>% 
  transmute(age = x, 
            metric = "recruit", 
            mean = predicted, 
            mean_lwr = conf.low, 
            mean_upr = conf.high)
surv_recruit_pred <- rbind(pup_surv_pred, pup_recruit_pred) %>% 
  mutate(metric = factor(metric, 
                         levels = c("surv", "recruit"), 
                         labels = c("Survival", "Recruitment")))

>>>>

sealdat <- read_csv(here::here("data/raw/128L pull 2023_12_05.csv"), 
                    show_col_types = FALSE) %>% 
  mutate(observed = if_else(observed == "B", "Breeder", "Non-breeder"), 
         observed_int = if_else(observed == "Breeder", 1, 0), 
         pup_survived = pupseeneveragain > 0) %>% 
  filter(age > 3, 
         year > 1987)
```

@@

```{r}
#| tbl-cap: str_glue("The results from breeding probability analyis. The random effect variance of animal id is {VarCorr(breeding_mod, digits = 3)[1]} and year was VarCorr(breeding_mod, digits = 3)[2].")
#| eval: true

@@

surv_recruit_data <- sealdat %>% 
  drop_na(pupID) %>% 
  filter(pupsex == "F",
         pupyearborn < 2016) %>% 
  mutate(pup_survived_dbl = ifelse(pup_survived, 1, 0)) %>% 
  group_by(age) %>% 
  mutate(n_pups = n()) %>% 
  ungroup() %>% 
  filter(n_pups >= 5)
pup_surv_model <- glmer(pup_survived_dbl ~ poly(age, 2) + (1 | animalID) + (1 | year),
                        data = surv_recruit_data, 
                        family = "binomial")
pup_surv_pred <- ggpredict(pup_surv_model, terms = c("age [all]")) %>% 
  as_tibble() %>% 
  transmute(age = x, 
            metric = "surv", 
            mean = predicted, 
            mean_lwr = conf.low, 
            mean_upr = conf.high)
pup_recruit_model <- glmer(puprecruited ~ poly(age, 2) + (1 | animalID) + (1 | year),
                           data = surv_recruit_data, 
                           family = "binomial")
pup_recruit_pred <- ggpredict(pup_recruit_model, terms = c("age [all]")) %>% 
  as_tibble() %>% 
  transmute(age = x, 
            metric = "recruit", 
            mean = predicted, 
            mean_lwr = conf.low, 
            mean_upr = conf.high)
surv_recruit_pred <- rbind(pup_surv_pred, pup_recruit_pred) %>% 
  mutate(metric = factor(metric, 
                         levels = c("surv", "recruit"), 
                         labels = c("Survival", "Recruitment")))
